%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{rinkal_resume}
\usepackage{fontawesome}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{Rinkal}{Agrawal}{ \href{mailto:agrawa55114l.rinkal.us@gmail.com}{agrawal.rinkal.us@gmail.com} \thinspace
| \thinspace St.Paul, MN \thinspace
| \thinspace 612.532.7639 \thinspace
| \thinspace
\faGithubAlt \thinspace \thinspace 
\faLinkedin \thinspace \thinspace 
\faMedium \thinspace : {/agrawalrinkal}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.30\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{University Of Minnesota}
\descript{B.S. in Computer Science}
\small May 2017  Graduate | CGPA: 3.64/4.0 \\
\small Dean's List recipient for all semesters
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Languages}
\vspace{1pt}
Java \textbullet{} 
Python \textbullet{}
Typescript \textbullet{}
Swift \textbullet{} \\
C\# \textbullet{} 
HTML5 \textbullet{}
CSS3 \textbullet{}
JavaScript \textbullet{} \\
C/C++ \textbullet{}
MySQL %\textbullet{}
\sectionsep

\vspace{1pt}
\subsection{Frameworks}
\vspace{1pt}
Angular 6 \textbullet{}
Node.js \textbullet{}
PyTorch \textbullet{}
Xcode \textbullet{}
Express.js \textbullet{}
Bootstrap4 \textbullet{}
MongoDB \textbullet{}
React \textbullet{}
.Net 
\sectionsep

\vspace{1pt}
\subsection{Strong Knowledge}
\vspace{1pt}
Microservice Architecture \textbullet{}
REST \textbullet{} \\
Unit Testing \textbullet{}
Product Ownership \textbullet{} \\
NPM packages \textbullet{}
Agile Methodology \textbullet{} \\
Github \textbullet{} 
Tomcat \textbullet{}
Eclipse %\textbullet{}
\sectionsep

\vspace{1pt}
\subsection{Working Knowledge}
\vspace{1pt}
Neural Networks(MLP, CNN, RNN, LSTM)  \textbullet{}
Redis \textbullet{}
Flask \textbullet{}
RabbitMQ \textbullet{}
Twilio API's \textbullet{}
AWS \textbullet{}
Firebase \textbullet{}
MVC \textbullet{}
MVVM \textbullet{} \\
Multi-threaded Programming  \textbullet{} \\
Google Cloud API's\textbullet{} 
PHP %\textbullet{}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research}
\runsubsection{Undergrad Researcher} \\
\location{U of M Software Engineering Center Aug '16 – Dec '16}
% \vspace{\topsep} % Hacky fix for awkward extra vertical space

% Fix to horizontally align the multi-line \textbullet{} and adds a horizontal space to the second line
\newlength\boxwid
\settowidth{\boxwid}{\indent\hspace{0.5cm}}

% Adds the horizontal space to the bullet point
% \begin{tightemize}
\hspace{0.2cm} \hangindent=\boxwid 
\textbullet{} Worked on a NASA project under Prof. Sanjai Rayadurgam to display the autonomous applications of a quad copter drone by using a pix hawk hardware with tweaked octocopter software. \\
% \end{tightemize}

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Coursework}
Advance Algo and Data structures \\
Intro to Deep Learning \\
Software Design and Development \\
Artificial Intelligence \\
Internet Programming \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Intrest
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Interests}
\textbullet{} Mentoring students w/ CoderDojo \\
\textbullet{} Networking events and webinars \\
\textbullet{} Reading and Writing blogs \\
\textbullet{} Outdoors, Roadtrips and Hiking \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.69\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Software Engineer ii }\hfill\  \location{Nov '18 – Present} 
\location{Software Engineer I \hfill June '17 - Nov '18}  
\location{CenturyLink}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Built a data-driven application using Angular6, and Java on node.js to provide a front-end for inventory, leading to 40\% less error tickets over 6 months. As a product owner, decided feature directions, worked with users to gather requirements and feedback.
\item Implemented an automation solution in Java for SD-WAN technology by working with different business units, resulting in decrease in device activation time from 30+ minutes to just over 2 minutes.
\item Built a server-side routing engine using javaScript and json on express.js to route the incoming traffic based on the request, resulting in over 20\% decrease in client server load.
\item Increased the legacy server engine efficiency by 4 folds by rewriting the algorithm using SNMP technology.
\end{tightemize}
\sectionsep

\runsubsection{Software Developer Intern} \\
\location{Design Ready Controls Inc. \hfill  June '16 – June '17}
\begin{tightemize}
\item Worked on windows desktop applications using C\# and .Net that helped electrical engineers better and faster design control panels, reducing the panel delivery time by almost 20\%.
\item Designed and implemented the UI for the android app for an R\&D project that let users see the field sensors data in real time using AWS.
\end{tightemize}
\sectionsep


% \runsubsection{Application Developer Intern} \\
% \location{College of Education and Human Development \hfill  May '16 – Aug '16}
% \begin{tightemize}
% \item Redesigned and implemented project website that lets anyone add subtitles to any video once provided with a video link; accessible at ant.umn.edu
% \item Worked on an android app that assists Google cardboard box.
% \end{tightemize}
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Spy}
\descript{| web app for monitoring team's success} 
\location{Independent @work, 9 weeks  \hfill | Angular6, Java}
\begin{tightemize}
\item Designed and built the app to let team members post their project successes.
\item Lets other people within the company view posted achievements and other project related statistics from an elegant dashboard.
\end{tightemize}
\sectionsep

\runsubsection{Top Tweets}
\descript{| US map visualization showing top tweets} 
\location{Independent, 2 weeks \hfill  | Java, Python, Apache-storm}
\begin{tightemize}
\item Built a US map visualization showing top tweets in the based on likes and re-tweets.
\item Integrated multiple open sourced bolts to achieve the output.
\end{tightemize}
\sectionsep

\runsubsection{Style Transfer}
\descript{| CNN to transfer image style} 
\location{Independent, 2 weeks  \hfill | Python, PyTorch}
\begin{tightemize}
\item Designed a Convolutional Neural Network using a pre-trained VGG19 model to transfer the style of one image onto the content of another image generating a completely new image.
\end{tightemize}
\sectionsep

\runsubsection{Video Messenger}
\descript{| Web app for hearing impaired students} 
\location{Non-Academic, 13 weeks, team of 4  \hfill | React}
\begin{tightemize}
\item Designed and built to conduct an on-line class of hearing impaired students by implementing video messaging recorded in sign language to help improve their university experience.
\end{tightemize}
\sectionsep

% \runsubsection{Bitcoin Tracker}
% \descript{| iOS app for tracking bitcoin prices} 
% \location{Independent project, 3 weeks \hfill  | Swift, MongoDB}
% \begin{tightemize}
% \item Designed to track bitcoin prices and it's market demand. Added a feature to provide customized notifications based on the user filled price range.
% \end{tightemize}
% \sectionsep

\runsubsection{Language Translator}
\descript{| CDAL to C++ Code translator} 
\location{Academic, 15 weeks, team of 2 \hfill  | C++}
\begin{tightemize}
\item  Built a compiler to translate 'Climate Data Analysis Language' code into C++ code using regular expressions. Extensively utilized unit testing to verify correctness.
\end{tightemize}
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
